Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-08-07 ms.tex
added ap labels to go with the vertically offset background aperture test

\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_voffset_background_phot_azlab04_rpf256_voffset_bsub_with_refpx_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{Ref Pixel-Corrected, 2048x256}
\fig{azlab_ratio_tser_voffset_background_phot_azlab04_rpf256_voffset_bsub_no_refpx_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{No Ref Pixels Used, 2048x256}}}
{\gridline{\fig{azlab_ratio_tser_voffset_background_phot_azlab04_rpf064_voffset_bsub_with_refpx_NRC64STRIPE1P5MA.pdf}{0.33\textwidth}{Ref Pixel-Corrected, 2048x64}
\fig{azlab_ratio_tser_voffset_background_phot_azlab04_rpf064_voffset_bsub_no_refpx_NRC64STRIPE1P5MA.pdf}{0.33\textwidth}{No Ref Pixels Used, 2048x64}}}
\caption{If a background aperture is vertically displaced from the source aperture, the reference pixels are important in reducing 1/f noise.}\label{fig:RefpixWithVertOffsetBackground}
\end{figure*}

>>>>

\begin{figure*}
\gridline{\fig{ap_labels_azlab04_rpf256_voffset_bsub_with_refpx487_NRCBSELINE0P9MA.pdf}{0.7\textwidth}{}}
\gridline{\fig{ap_labels_azlab04_rpf256_voffset_bsub_with_refpx489_NRCBSELINE0P9MA.pdf}{0.7\textwidth}{Apertures for 2048x256 stripe}}
{\gridline{\fig{azlab_ratio_tser_voffset_background_phot_azlab04_rpf256_voffset_bsub_with_refpx_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{Ref Pixel-Corrected, 2048x256}
\fig{azlab_ratio_tser_voffset_background_phot_azlab04_rpf256_voffset_bsub_no_refpx_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{No Ref Pixels Used, 2048x256}}}
{\gridline{\fig{azlab_ratio_tser_voffset_background_phot_azlab04_rpf064_voffset_bsub_with_refpx_NRC64STRIPE1P5MA.pdf}{0.33\textwidth}{Ref Pixel-Corrected, 2048x64}
\fig{azlab_ratio_tser_voffset_background_phot_azlab04_rpf064_voffset_bsub_no_refpx_NRC64STRIPE1P5MA.pdf}{0.33\textwidth}{No Ref Pixels Used, 2048x64}}}
\caption{If a background aperture is vertically displaced from the source aperture, the reference pixels are important in reducing 1/f noise.}\label{fig:RefpixWithVertOffsetBackground}
\end{figure*}
